### 2024-05-26 getting-started.qmd
20240525 - figure label and caption

```{r}
pbp_regularSeason <- nfl_pbp %>% 
  dplyr::filter(
    season == 2023,
    season_type == "REG") %>%
  dplyr::filter(!is.na(posteam) & (rush == 1 | pass == 1))

>>>>

```{r}
#| label: fig-plotDefOffEPA
#| fig-cap: "2023 NFL Offensive and Defensive EPA per Play"

pbp_regularSeason <- nfl_pbp %>% 
  dplyr::filter(
    season == 2023,
    season_type == "REG") %>%
  dplyr::filter(!is.na(posteam) & (rush == 1 | pass == 1))
